Resource Buying Games

### 2017-04-02 paper.tex
started on non-matroid strategy spaces

>>>>

\section{Non-Matroid Strategy Spaces}
Finally, we consider in this section non-matroid strategy spaces. Specifically,
we present a construction which illustrates how to obtain a weighted two player
resource buying game with marginally non-increasing cost functions which does
not posses a PNE starting from a non-matroid anti-chain $S$. This implies that
matroids are exactly the structures to consider using marginally non-increasing
cost functions since other structures cannot guarantee the existence of PNEs.
